---
title       : Diamond Search Portal 
subtitle    : One stop shop for your search
author      : Surbhi
job         : Data Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : zenburn      # 
ext_widgets: {rCharts: ["libraries/highcharts", "libraries/nvd3", "libraries/morris"]} 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}

---

## What is Diamond Search Portal?

The **Diamond Search Portal** allows users to gain some insight at some 54,000 round-cut diamonds out there.

The portal allows you to search and analyze data for diamonds based on 4Cs and to compare prices and dimensions with just a few clicks. 

You don't have to trouble yourself with dealing with jewelers and diamond dealers, we have done to the leg work for you!

--- .class #id 

## Who should use Diamond Search Portal?

Are you a wholesale retailer, a to-be-spouse or just a diamond lover looking to find that perfect rock that matches your budget and your specifications? 

If yes,  then **Diamond Search Portal** is for you.

- You will be able to conduct your search based a number of criteria. 

- You will be able to visualize and analyze the data in numerous ways. 

- You will be able to download the data that you searched for as a .csv file.


------ &twocol w1:40% w2:60%

## Portal Interface - The two panels

*** {name: left}

Side Panel contains the following filters:  

- Price 
- Cut 
- Color 
- Clarity 
- Carat


*** {name: right}

Main Page is divided into the following tabs to allow you to efficiently obtain the information that you desire:  

- Table: Provides a listing of the data.         
- Summary: Provides a high-level summary of the data.     
- Plot: Allows you to create a scatter plot based on selected X- and Y-variables.                        
- Pie Chart: Beautifully displays information regarding Cut, Color and Clarity of the diamonds and their count.

--- &twocol w1:40% w2:60%

## Output Examples  

***{name: left}

<h3>Plot Example:</h3>

```{r, echo=FALSE}
library(ggplot2)
data <- diamonds
    colnames(data) <- c("Carat", "Cut", "Color", "Clarity", "Depth %", 
                        "Table", "Price", "Length", "Width", "Depth")
plot(data$Carat, data$Price, col = as.integer(unique(data$Carat)), xlab="Carat", ylab="Price")
```

***{name: right}

<h3>Pie Chart Example:</h3>

```{r setup, message = F, echo = F}
library(rHighcharts)
require(rCharts)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = T)
```
```{r chart1, echo=FALSE}
e<-Highcharts$new()
e$title(text = "Diamond Cut", float="left")
e$data(x=c("Fair", "Good", "Very Good",  "Premium", "Ideal"), y=c(1610, 4906, 12082, 13791, 21551), type="pie", name = "Count", size=150)
e
```
    


